### 2020-03-23 README.Rmd
add binder and actions

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/yichun33/archyconfgender/master?urlpath=rstudio)
[![R build status](https://github.com/yichun33/archyconfgender/workflows/R-CMD-check/badge.svg)](https://github.com/yichun33/archyconfgender/actions)
